Hypertension and microbiome

### 2019-01-02 rrbiome.Rmd
PCA ready?

```{r pca percentage}
(pca.prcomp$sdev / sum(pca.prcomp$sdev)) %>% head %>% kable
```

Labels for PCA plot containing the

```{r pca labels}
pca.percentage <- round(pca.prcomp$sdev / sum(pca.prcomp$sdev) * 100, 2)
pca.labels <- paste0(colnames(pca.prcomp$x), " (", paste0(as.character(pca.percentage), "%", ")"))
```

```{r PCA plots categorical, fig.width = 10, fig.height = 10, dpi = 300, eval = FALSE}
ggplot((cbind(meta(pseq_filtered), prcomp$x[,1:2]) %>%
        select(PC1, PC2, BP_TREAT, CURR_SMOKE, DIAB, BL_USE_RX_C09, Q57X,
               BL_USE_RX_C03, BL_USE_RX_C07, BL_USE_RX_C08, HYPERTENSION, SEX) %>%
        gather(Covariate, Value, -PC1, -PC2)), 
       aes(x=PC1, y=PC2)) +
    facet_wrap(~Covariate, ncol=2, scales = "free") +
    geom_point(aes(color = Value), size = 0.5) +
    scale_color_brewer(palette="Dark2") +
    xlab(pca.labels[1]) +
    ylab(pca.labels[2]) +
    ggplot2::theme_minimal()

```{r PCA plots continuous, fig.width = 10, fig.height = 10, dpi = 300,  eval = FALSE}

ggplot((cbind(meta(pseq_filtered), prcomp$x[,1:2]) %>%
        select(PC1, PC2, BL_AGE, SYSTM, DIASM, BMI, MAP, PULSEPRESSURE) %>%
        gather(Covariate, Value, -PC1, -PC2)), 
       aes(x=PC1, y=PC2)) +
    facet_wrap(~Covariate, ncol=2, scales = "free") +
    geom_point(aes(color = Value), size = 0.5) +
    scale_color_gradientn(colours = rainbow(12)) +
    xlab(pca.labels[1]) +
    ylab(pca.labels[2]) +
    ggplot2::theme_minimal()

>>>>

Proportion of variance for main PC axis

```{r pca percentage}
pca.eigs <- pca.prcomp$sdev^2
pca.percentage <- 100 * eigs /sum(eigs)
pca.labels <- sprintf("%s (%.2f %%)", colnames(pca.prcomp$x), pca.percentage)
pca.percentage %>% head %>% kable
```

PCA plot for hypertension

```{r PCA plots continuous, fig.width = 10, fig.height = 4, dpi = 300}
ggplot(cbind(meta(pseq.species), pca.prcomp$x[,1:2]), aes(x=PC1, y=PC2)) +
    geom_point(aes(color = HYPERTENSION), size = 0.2) +
    xlab(pca.labels[1]) +
    ylab(pca.labels[2]) +
    scale_color_brewer(palette="Dark2") +
    ggplot2::theme_minimal() 
```
